---
title: "Weekend Homework - Model Building"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

# MVP

We've looked at a few different ways in which we can build models this week, including how to prepare them properly. This weekend we'll build a multiple linear regression model on a dataset which will need some preparation. The data can be found in the data folder, along with a data dictionary

We want to investigate the avocado dataset, and, in particular, to model the `AveragePrice` of the avocados. Use the tools we've worked with this week in order to prepare your dataset and find appropriate predictors. Once you've built your model use the validation techniques discussed on Wednesday to evaluate it. Feel free to focus either on building an *explanatory* or a *predictive* model, or both if you are feeling energetic!

As part of the MVP we want you not to just run the code but also have a go at **intepreting the results** and write your thinking in comments in your script.

**Hints and tips**

* `region` may lead to many dummy variables. Think carefully about whether to include this variable or not (there is no one 'right' answer to this!)
* Think about whether each variable is *categorical* or *numerical*. If categorical, make sure that the variable is represented as a factor.
* We will not treat this data as a time series, so `Date` will not be needed in your models, but can you extract any useful features out of `Date` before you discard it?
* If you want to build a predictive model, consider using either `leaps` or `glmulti` to help with this.

I dropped the small bags, large bag, extra large bags and total bags, relying 
on total volume as an indicator of volume sold. Dropped the identifying
X1 column. Extracted the month out of date and recoded this into seasons 
(1 = Spring, 2 = Summer, 3 = Autumn, 4 = Winter). Dropped the date column. 
Filtered region down to West, Midsouth, Northeast and Southeast and turned
these into dummy variables, dropping first dummy. I coerced the 
season variable to factor. 

```{r}
library(tidyverse) 
library(fastDummies) 
library(janitor) 
library(lubridate) 

avocados <- read_csv("data/avocado.csv") %>% 
  select(-c("X1", "Small Bags", "Large Bags", "XLarge Bags", "Total Bags")) %>% 
  clean_names() %>% 
  mutate(date = month(date)) %>% 
  mutate(season = lubridate::quarter(date)) %>% 
  mutate(type = as.factor(type)) %>% 
  select(-date) %>% 
  filter(region == c("West", "Midsouth", "Northeast", "Southeast")) %>% 
  dummy_cols(select_columns = "region", remove_first_dummy = TRUE, 
             remove_selected_columns = TRUE) %>% 
  mutate(season = as.factor(season)) 

str(avocados) 
```

I checked for any variables that are highly correlated with another. There were 
not any variables that could be used to compute other variables. 

```{r}
alias(average_price ~ ., data = avocados) 
```



```{r}
library(GGally) 

ggpairs(avocados) 
```

There appears to be a negative relationship between total volume avocados sold 
and average price. It appears that for every increase in avocados sold there is 
a -0.0000001136 decrease in price, which is a statisticaly significant 
difference. R squared score of 0.5552. 

```{r}
avocados %>% 
  ggplot(aes(x = average_price, y = total_volume)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) 

model_a <- lm(average_price ~ total_volume, data = avocados) 

summary(model_a)  

par(mfrow = c(2,2)) 

plot(model_a) 

library(modelr)

avocados_remaining_resid <- avocados %>%
  add_residuals(model_a) %>%
  select(-c("average_price", "total_volume")) 
```

Exploring the season impact. It looks like the price may increase in autumn 
and be lowest in spring. This may be related to the fact sales are possibly 
related to the different seasons, since it has already been established 
sales are a predictive variable, accounting for 55% of the variance in 
average price, assuming other factors are kept the same. 

```{r}
avocados %>%
  ggplot(aes(x = season, y = average_price)) + 
  geom_boxplot() 
```

We can see the price is highest in Autumn (July, August and September). 

```{r}
ggpairs(avocados_remaining_resid) 

model_b <- lm(average_price ~ total_volume + season, data = avocados) 

summary(model_b) 

par(mfrow = c(2,2)) 

plot(model_b) 

plotModel(model_b) 
```

```{r}
anova(model_a, model_b) 
```

```{r}
model_c <- lm(average_price ~ total_volume + season + region_Northeast, 
              data = avocados) 

summary(model_c) 

par(mfrow = c(2,2)) 

plot(model_c)  
```

```{r}
anova(model_b, model_c) 
``` 

```{r}
avocados_remaining_resid_two <- avocados %>% 
  add_residuals(model_c) %>% 
  select(-c(average_price, total_volume, season, region_Northeast)) 

avocados_remaining_resid_two %>% 
  ggpairs() 
```

This model accounts for 70% of variance in the price of avocados. It includes 
the total volume of avocados sold, the season they were sold in, being sold 
in the North East region and the year they were sold. The more sold, the lower 
the price goes. The season is important in this model because the price of 
avocados is highest in autumn. The other seasons do have a statistically 
significant impact on the price too, the increase is just smaller than 
in autumn. It can be seen that the biggest regional difference in 
price can be seen in the North East. This region has the biggest improvement in 
adjusted r-squared. The year has a statistically significant relationship 
with price. The price is highest in 2017. The diagnostics of this model 
look okay. 

```{r}
model_d <- lm(average_price ~ total_volume + season + region_Northeast 
              + year, data = avocados) 

summary(model_d) 

par(mfrow = c(2,2)) 

plot(model_d)   
```

```{r}
anova(model_c, model_d) 
```

After doing the ggpairs analysis on the new residuals, it does not appear the 
model will be statistically significantly improved by introducing another 
variable into the model. 

```{r}
avocados_remaining_resid_three <- avocados %>% 
  add_residuals(model_d) %>% 
  select(-c(average_price, total_volume, season, region_Northeast, year)) 

avocados_remaining_resid_three %>% 
  ggpairs() 
```