---
title: "R Notebook"
output: html_notebook
---

#Connecting R to a DB using a source file 

#Keeping credentials secure not pushing to github 

```{r}
library(RPostgres) 
```

#Now source in our credentials file and use rm() for hiding them afterwards 

```{r}
source("~/omni_credentials.R") 
```

```{r}
source("~/omni_credentials.R") 
db_connection <- dbConnect(
  drv = Postgres(), 
  user = omni_username, 
  password = omni_password, 
  dbname = "omni_pool", 
  host = "db-postgresql-lon1-94437-do-user-4831272-0.a.db.ondigitalocean.com", 
  port = 25061, 
  bigint = "numeric") 

rm(omni_username, omni_password) 
```

```{r}
dbListTables(conn = db_connection) 
```

```{r}
dbListFields(conn = db_connection, name = "employees")
```

#dbGetQuery(): 
#Sends the query 
#It retrieves the results 
#It clears the results set 

#Pattern for dealing with big data in "chunks" 

```{r}
data <- dbGetQuery(
  conn = db_connection, 
  statement = "SELECT * FROM employees") 

data 
```

```{r}
class(data)
```

```{r}
nrow(data)
```

```{r}
result_set <- dbSendQuery(
  conn = db_connection, 
  statement = "SELECT * FROM employees"
) 

class(result_set) 

```

```{r}
first_10 <- dbFetch(res = result_set, n = 10) 

first_10 
```

```{r}
next10 <- dbFetch(res = result_set, n = 10) 

next10
```

#Can force it to give all the remaining records 

```{r}
all_remaining <- dbFetch(res = result_set, n = -1) 

nrow(all_remaining) 
```

```{r}
dbClearResult(res = result_set) 
```

#Native SQL chunk in R notebook 

```{sql, connection = db_connection} 
SELECT * 
FROM employees 
LIMIT 10 
```

```{sql, connection = db_connection, output.var = "pay_details"} 
SELECT * 
FROM pay_details
```

```{r}
pay_details 
```

#Changing the iban column to lower case 

```{r}
library(tidyverse) 
pay_details %>% 
  mutate(iban = str_to_lower(iban))
```

```{r}
dbDisconnect(conn = db_connection)
```

