---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(dplyr) 
```

```{r}
movies_data <- read_csv("data/movies.csv")
head(movies_data, 10) 
view(movies_data) 
```
#Investigating how many rows are dropped if you remove na's 
```{r}
nrow(movies_data) - nrow(is.na(movies_data))
```

#A lot of interesting stuff in there! But for now, we are only interested in the movies’ titles, their runtime as well as their budget. Select the three columns that contain this information and save them into a new variable called movies_selected. Hint: you will have to make a choice between original_title and title.
```{r}
movies_selected <- select(movies_data, title, runtime, budget) 
movies_selected 
```

#Ok, now take your subsetted data movies_selected, and count the number of missing values in each column 
#My answer 
```{r}
movies_selected %>% 
  summarise(count = sum(is.na(movies_selected)))
```

#Homework answer 
```{r}
movies_selected %>% 
  summarise(na_title = sum(is.na(title)),
            na_runtime = sum(is.na(runtime)),
            na_budget = sum(is.na(budget))) 
```

#There’s not too many NAs, but there are actually quite a few movies with a runtime of 0 in this dataset. Since it’s impossible for a movie to have a runtime of 0, use the function na_if to convert runtimes of length 0 into NAs. Save this into a new variable called movies_runtime. Then count how many missing values there are now in the column runtime 
#My answer 
```{r}
movies_runtime <- 
  movies_selected %>%
  mutate(movies_runtime = 
           na_if(runtime, "0")) 
sum(is.na(movies_runtime))
```

#Homework answer 
```{r}
movies_runtime <- 
  movies_selected %>% 
  mutate(movies_runtime = na_if(runtime, "0"))
summarise(count = sum(is.na(movies_runtime)))
```

#Impute the missing values in runtime with the median runtime using coalesce and save this into a new variable called movies_imputed. There should now be no missing values in the column runtime - check this to make sure 
```{r}
movies_imputed <- 
  movies_selected %>% 
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE))) 
movies_imputed 

is.na("runtime")
sum(is.na("runtime"))
```

#Finally, use the slice_min and slice_max functions on movies_imputed to get the movies with the 10 shortest and 10 longest runtime 
#Variable movies_imputed was not working because slice works on column titles and movies_imputed contains various types of variables. 
```{r}
movies_selected %>%
  slice_max(runtime, n = 10)
```
#Does this by distinct values so it produces all 35 values 
```{r}
movies_selected %>%
  slice_min(runtime, n = 10) 
```


#impute everything with a budget below $100 with the median budget using is_else and overwrite movies_imputed 
#Homework solutions 
```{r}
movies_imputed <- movies_selected %>%
  select(budget) %>% 
  mutate(budget = if_else(budget < 100, median(budget), budget)) 
head(movies_imputed, 10) 
```

#Using pipes wrong 
```{r}
movies_imputed <- movies_selected %>%
  select(budget) %>%
  if_else(budget < 100, coalesce(budget, median(budget, na.rm = TRUE)), budget) 
```

```{r}
movies_imputed <- if_else(budget < 100, coalesce(budget, median(budget, na.rm = TRUE)), budget)
```

#Good example of pipes 
```{r}
amount_spent <- c(9.1, 8.55, 14.32, 14.17, 14.34, 7.97, 9.79, 11.47 ,12.44)

category <- c("Lunch", "Dinner", "Lunch", "Lunch", "Cinema", "Drinks",
  "Lunch", "Lunch", "Dinner")
  
my_week_of_spending <- tibble(
  total_amount_spent = amount_spent, 
  spending_category = category)
  
str(my_week_of_spending)

my_week_of_spending %>%
  summarise(my_week_of_spending, sum(amount_spent)) 

#Not summarising the week of spending here, so the total amount spent for each "Lunch" category is not shown. This pipe only shows the total sum for "Lunch" because we did not ask for a summary of week of spending. 

my_week_of_spending %>%
  filter(spending_category == "Lunch") %>%
  summarise(sum(total_amount_spent)) 
```

#Question 1Using case_when, create a new column called budget_type and label budgets as follows: #Budgets below 12 million as ‘Small budget’
#Budgets between 12 and 40 million as ‘Medium budget’
#Budgets 40 millions and above as ‘Big budget’
#Save this into a new variable called movie_budgets. 
```{r}
movie_budgets <- movies_data %>%
  mutate(
    movie_budget = case_when(budget < 12000000 ~"Small Budget", 
              budget < 40000000 ~ "Medium Budget", 
              budget >= 40000000 ~ "Large Budget")) 
movie_budgets 
```

#Take the original dataset with all the variables. Using across and where, summarise the number of missing values, first across all columns of type character, and then across all columns of type numeric.

```{r}
movies_data %>%
  summarise(across(where(is.numeric), ~sum(is.na(.x))))
```

```{r}
movies_data %>% 
  summarise(across(where(is.character), ~sum(is.na(.x))))
```

```{r}
summarise(across(where(is.character), ~sum(is.na(.x))))