---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse) 
library(CodeClanData)

revenue_breakdown <- qb_revenue_breakdown 
monthly_sales <- qb_monthly_sales 
competitors <- qb_competitors 
device_data <- qb_device_data 
```

```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```


Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset. 

```{r}
ggplot(revenue_breakdown) + 
  aes(x = Product, y = Revenue, fill = Year) + 
  geom_col(position = "stack") + 
  labs(title = "Revenue sources over the last two years", size = 12) + 
  scale_fill_manual(
    values = c(
      "2018" = "#E89FE9",
      "2019" = "#B6A7B5"
    ) 
  ) 
```

Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset. 

```{r}
sales_subset <- monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") 
```

```{r}
ggplot(sales_subset) + 
  aes(x = Date, y = Amount) + 
  geom_line() + 
  labs(title = "Kwikbit Sales", size = 12) + 
  ylab("Sales") 
```
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales. 

```{r}
ggplot(monthly_sales) +  
  aes(x = Date, y = Amount, colour = Cashflow) + 
  geom_line() + 
  labs(title = "Monthly revenue and costs over the last year", size = 12) + 
  scale_colour_manual(
    values = c(
      "Cost" = "#E89FE9",
      "Kwikbit Unit 1 Sales" = "#B6A7B5",
      "Total Revenue" = "#F9A472"
    ) 
  ) 
``` 

Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors. 

```{r}
ggplot(competitors) + 
  aes(x = Year, y = Revenue, colour = Company) + 
  geom_area() + 
  labs(title = "Personal fitness tracker sales over the last 5 years", size = 12) + 
  scale_colour_manual(
    values = c(
      "Competitor 1" = "#50434F",
      "Competitor 2" = "#B6A7B5",
      "Competitor 3" = "#F9A472", 
      "Competitor 4" = "#E89FE9"
    )
  ) 
```

Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines. 

```{r}
ggplot(competitors) + 
  aes(x = Company, y = Revenue) + 
  geom_line() + 
  geom_point() + 
  labs(title = "Competitors sales", size = 12) 
```

Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data. 

```{r}
ggplot(device_data) + 
  aes(x = hours, y = counts, colour = device) + 
  geom_line() + 
  facet_wrap(~ id) + 
  labs(title = "Steps measured by quikbit1 versus competitors", 
       subtitle = "Grouped by individuals") + 
  scale_colour_manual(
    values = c(
      "quikbit1" = "#E89FE9",
      "competitor1" = "#50434F",
      "competitor2" = "#B6A7B5",
      "competitor3" = "#F9A472"
    )
  ) 

```

