---
title: "R Notebook"
output: html_notebook
---

1. Tidy up the data ready for regression:

* You might like to think about removing some or all of date, id, sqft_living15,
sqft_lot15 and zipcode (lat and long provide a better measure of location in 
any event). 
* Have a think about how to treat waterfront. Should we convert its type? 
* We converted yr_renovated into a renovated logical variable, indicating 
whether the property had ever been renovated. You may wish to do the same.
* Have a think about how to treat condition and grade? Are they interval
or categorical ordinal data types? 

mutate(view = as.logical(waterfront)) %>% 

```{r}
library(tidyverse) 
library(janitor) 
library(lubridate) 
library(modelr) 
library(GGally) 

houses <- read_csv("data/kc_house_data.csv") %>% 
  select(-c(id, sqft_living15, sqft_lot15, zipcode, date, sqft_above)) %>% 
  mutate(waterfront = as.logical(waterfront)) %>% 
  mutate(yr_renovated = as.logical(yr_renovated)) 

houses 
```

2. Check for aliased variables using the alias() function (this takes in a 
formula object and a data set). [Hint - formula price ~ . says ‘price varying 
with all predictors’, this is a suitable input to alias()]. Remove variables 
that lead to an alias. Check the ‘Elements of multiple regression’ lesson 
for a dropdown containing further information on finding aliased variables in 
a dataset. 

```{r}
model_alias <- lm(price ~ ., data = houses) 

alias(model_alias) 
```

3. Systematically build a regression model containing up to four main effects 
(remember, a main effect is just a single predictor with coefficient),testing 
the regression diagnostics as you go. 

* Splitting datasets into numeric and non-numeric columns might help ggpairs() 
run in manageable time, although you will need to add either a price or 
resid column to the non-numeric dataframe in order to see its 
correlations with the non-numeric predictors. 

```{r}
houses_numeric <- houses %>% 
  select(price, bedrooms, bathrooms, sqft_living, sqft_lot, sqft_basement, 
         floors, condition, grade, yr_built, lat, long, view) 

ggpairs(houses_numeric) 
```

```{r}
houses_nonnumeric <- houses_clean %>% 
  select_if(function(x) !is.numeric(x)) 

houses_nonnumeric 

houses_nonnumeric$price <- houses_clean$price 

ggpairs(houses_nonnumeric) 
```

Square foot of the living space - price increases by 280 for each increase in 
square foot. It accounts for 49% of variance in price. 

```{r}
model_1 <- lm(price ~ sqft_living, data = houses) 

summary(model_1) 

par(mfrow = c(2, 2)) 

plot(model_1) 
```

Searching for the predictors not yet in our model by adding the residuals. 

```{r}
remaining_residuals <- houses %>% 
  add_residuals(model_1) %>% 
  select(-c("price", "sqft_living")) 

remaining_residuals %>% 
  ggpairs() 
```


```{r}
model_2 <- lm(price ~ sqft_living + yr_built, data = houses) 

summary(model_2) 

par(mfrow = c(2, 2)) 

plot(model_2) 
```

There is a statistically significant difference if the model includes year built 
so that can be kept in the model. 

```{r}
anova(model_1, model_2) 
```

```{r}
remaining_residuals2 <- houses %>% 
  add_residuals(model_2) %>% 
  select(-c("price", "sqft_living", "yr_built")) 

remaining_residuals2 %>% 
  ggpairs()  
```

Visualising the interaction between view and waterfront. 

```{r}
coplot(price ~ view | waterfront, data = houses, columns=6) 
```


```{r}
model_3 <- lm(price ~ sqft_living + yr_built + view:waterfront, data = houses) 

summary(model_3) 

par(mfrow = c(2, 2)) 

plot(model_3) 
```

```{r}
anova(model_2, model_3) 
```

```{r}
library(relaimpo) 
```

```{r}
calc.relimp(model_3, type = "lmg", rela = TRUE) 
```       
```{r}
library(lm.beta) 

model_3_betas <- lm.beta(model_3)  

summary(model_3) 
```

