---
title: "R Notebook"
output: html_notebook
---

In this homework we’ll use the msleep data set provided in the ggplot package. It concerns the sleeping patterns of various types of mammal. 

```{r}
library(tidyverse) 
library(infer) 

sleep <- (msleep)
```

1.1 Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies. 

```{r}
observed_stat <- sleep %>% 
  summarise(mean_sleep = mean(sleep_total)) 

observed_stat 
```

```{r}
null_distribution <- sleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7.0) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean") 

null_distribution 
```

```{r}
null_distribution %>% 
  visualise() + 
  shade_p_value(obs_stat = observed_stat, direction = "both") 
```

```{r}
p_value <- null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "both") 

p_value 
```

In this case we can reject our null hypothesis that jabberwockies and the animals in the sample sleep 7 hours a night. Our p value was under 0.05, indicating a statistically significant difference between the average amount of sleep between jabberwockies and animals in our sample. 

1.2 Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average. 

```{r}
filtered_sleep <- sleep %>% 
  filter(vore == "omni" | vore == "herbi") 

filtered_sleep 
```

```{r}
filtered_sleep %>% 
  group_by(vore, sleep_total) %>% 
  summarise(sum = n()) %>% 
  summarise(count = sum(sum))
```


```{r}
filtered_sleep %>% 
  ggplot(aes(sleep_total, vore)) + 
  geom_boxplot() + 
  coord_flip() 
```

```{r}
null_distribution <- filtered_sleep %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi")) 
```

```{r}
observed_stat <- filtered_sleep %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
```

```{r}
null_distribution %>% 
  visualise() + 
  shade_p_value(obs_stat = observed_stat, direction = "greater")
```

```{r}
p_value <- null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "greater") 

p_value 
```

In this question we failed to reject the null hypothesis because our p value was over 0.05. Omnivores did not statistically significantly sleep a greater amount on average than herbivores. 

1.3 Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%. 

```{r}
filtered_conservation <- sleep %>% 
  mutate(is_domesticated = conservation == "domesticated") 

filtered_conservation 
```

```{r}
null_distribution <- filtered_conservation %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "simulate") %>% 
  calculate(stat = "prop") 
```

```{r}
observed_statistic <- filtered_conservation %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  calculate(stat = "prop") 

observed_statistic 
```

```{r}
p_value <- null_distribution %>% 
  get_p_value(obs_stat = observed_statistic, direction = "greater") 

p_value 
```

Given the p value is smaller than 0.05, we can reject the null hypothesis, which is to say that the proportion of domesticated animals in the subset is greater than 5%. 

2.1 You work for a independent coffee shop. You’ve performed a small survey in the local town and found that 40% of the people you randomly asked were aware of your shop in the town. You then conduct a marketing campaign by flyering local venues and targeting advertisements on social media. Finally you conduct a second small random survey in the town, asking if people are aware of your coffee shop. You want to test the hypothesis that the campaign has significantly increased awareness of the shop. 

N0: The awareness before and after the campaign is the same. 
Na: The awareness after the campaign is statistically significantly greater than before. 

H0: μdiff = 0 
Ha: μdiff != 0 

A bootstrap method would be used. 

2.2 You work for a website design company and have performed an A/B test on the position of a banner on a website page promoting a particular item. 

H0: There is no difference in the proportion of users that click on the banner on site A or B. 
Ha: There is a difference in the proportion of users that click on the banner on site A or B.  

H0: μ1−μ2 = 0  
Ha: μ1−μ2 != 0 

A permute method would be used to find the null distribution. 

2.3 You work as an analyst for a car manufacturing company - they have specific standards they must meet for standards and regulation purposes. You have been asked to check the quality control of the manufacture of a particular car part. The part must have a width of 145mm, with a small (given) level of tolerance. You have been given data on a sample of 1,000 parts produced over the period of a week. 

H0: μ0 = 145 
Ha: μ0  != 145 

H0: The sample mean is not equivalent to 145mm. 
Ha: The sample mean is not equivalent to 145mm. 

A bootstrap method would be used to find the null distribution. 

3.1 Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07 

There wasn't a statistically significant increase in awareness after the marketing campaign. The null hypothesis wasn't rejected. 

3.2 Website company problem. Significance level: 0.01, p-value: 0.006 

There was a statistically significant difference in the proportion of clicks on site A and B. This rejects the null hypothesis that there was no difference in the proportion of clicks in the two sites and supports the alternative hypothesis. 

3.3 Manufacturing company problem. Significance level: 0.05, p-value: 0.55 

There was not a statistically significant difference between the sample and 45mm. This fails to reject the null hypothesis but is good for the quality control of the sample of parts. 

Extension 

```{r}
transactions <- read_csv("data/online_retail_subset.csv") %>% 
  janitor::clean_names() 

head(transactions)
```

1.1 Calculate the support for item A. 

0.003666667	

```{r}
support_a <- transactions %>% 
  summarise(prob = sum(stock_code == "22469") / n()) 
```

1.2 Calculate the support and confidence for rule A -> B 

 Support: 0.004133333 
 
 Confidence: 1.127273 

```{r}
transactions %>% 
 filter(stock_code == "22469" | stock_code == "21110") %>% 
  summarise(sum = n()) 
```

```{r}
support_a_n_b <- 124/30000 
```

conf(A→B)=P(A and B being purchased together)P(A being purchased) 

```{r}
confidence_a_n_b <- 0.004133333 / 0.003666667	 
```


1.3 Calculate the lift for (A→B) 

2415.584 

```{r}
support_b <- transactions %>% 
  summarise(prob = sum(stock_code == "21110") / n()) 

support_b 
```

```{r}
lift <- support_a_n_b / a_x_b 
``` 

