---
title: "R Notebook"
output: html_notebook
---

You are given a cut of a database containing details of mobile phones and their customer reviews on an online shopping site in file 20190928-items.csv. Each row in the data corresponds to one model of mobile phone. Use the data to answer the following questions. 

As part of the MVP we want you not to just run the code but also have a go at intepreting the results - this is the main learning objective from this homework. Don’t worry if you aren’t sure, it’s ok to get it wrong, but give it a go, through trying we will learn. 

```{r}
library(tidyverse) 
library(janitor) 
```


```{r}
mobile_phones <- read_csv("data/20190928-items.csv") %>% 
  clean_names() 

mobile_phones 
```

Find the brand with the highest numbers of phones in the dataset. 

Samsung has the most phones with 397. 

```{r}
mobile_phones_filtered <- mobile_phones %>% 
  group_by(brand, title) %>% 
  summarise(total = n()) %>% 
  summarise(total = sum(total)) %>% 
  arrange(desc(total))
  
mobile_phones_filtered 
   
``` 

For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. 

Do you think the normal distribution provides a good model of these ratings? 

```{r}
mobile_phones %>% 
  mutate(f_l = dunif(x = rating, min = 1, max = 5)) %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating, y = f_l)) +
  geom_line() +
  ylim(0, 1) + 
  xlab("Rating") + ylab("Probability Density") 
```

```{r}
mobile_phones %>% 
  ggplot(aes(x = rating, y = f_l)) +
  geom_line() +
  ylim(0, 1) + 
  xlab("Rating") + ylab("Probability Density") 
``` 

```{r}
mobile_phones_statistics <- mobile_phones %>%
  filter(brand == "Samsung") %>%
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
mobile_phones_statistics 
```

```{r}
mobile_phones %>% 
  filter(brand == "Samsung") %>% 
  group_by(total_reviews) %>% 
  summarise(count = sum(total_reviews)) %>% 
  summarise(count2 = sum(count))
  
```

3118 


```{r}
mobile_phones %>% 
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 20) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = mobile_phones_statistics$mean, 
      sd = mobile_phones_statistics$sd
    ),
    col = "red"
  )
```

The normal distribution is quite a good fit for this data. 

We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. 

Compare these proportions with those you expect for a normal distribution. 

I can't figure out how to calculate the second and third standard deviations but given the first standard deviation proportion is slightly below the normal distribution I would think they will all be slightly lower. 

```{r}
one_sd <- mobile_phones %>%
  filter(rating >= mobile_phones_statistics$mean - mobile_phones_statistics$sd) %>%
  filter(rating <= mobile_phones_statistics$mean + mobile_phones_statistics$sd) %>%
  summarise(prob_within_1sd = n() / nrow(mobile_phones_statistics)) 

one_sd 
```

```{r}
two_sd <- mobile_phones %>%
  filter(rating > mobile_phones_statistics$mean - mobile_phones_statistics$sd) %>% 
  summarise(prob_within_2sd = n() / nrow(mobile_phones_statistics)) 

```

```{r}
three_sd <- mobile_phones %>%
  filter(rating <= mobile_phones_statistics$mean - mobile_phones_statistics$sd) %>% 
  summarise(prob_within_3sd = n() / nrow(mobile_phones_statistics)) 
```

