---
title: "R Notebook"
output: html_notebook
---

Read the cleaned data into R 

```{r}
library(tidyverse) 
library(dplyr) 
```

```{r}
clean_data <- read_csv("clean_homework_meteorite_data")
```

Find the names and years found for the 10 largest meteorites in the data 

```{r}
clean_data %>% 
  arrange(desc(mass_g)) %>% 
  head(10) 
```
```{r}
sum(is.na(clean_data$mass_g)) 
sum(clean_data$mass_g) 
is.numeric(clean_data$mass_g)
```

Names (Highest to lowest): Hoba, Cape York, Campo del Cielo, Canyon Diablo, Armanty, Gibeon, Chupaderos, Mundrabilla, Sikhote-Alin, Bacubirito 
Years (Highest to lowest): 1920, 1918, NA, 1891, 1898, 1836, 1852, 1911, 1947, 1863 

Find the average mass of meteorites that were recorded falling, vs. those which were just found 

Using variables , filter by fall status and calculate mean (as a test) 

```{r}
temp_df <- clean_data %>%
  filter(fall == "Found")
mean(temp_df_df$mass_g, na.rm = TRUE)
```

Alternate method, using group by rather than filter .This is more elegant than above

```{r}
clean_data %>% 
  group_by(fall) %>%
  summarise(indv_mean = mean(mass_g))
  
```
Find the number of meteorites in each year, for every year since 2000 

This approach uses group_by and a filter, with n() to perform the count 

```{r}
clean_data %>%
  group_by(year) %>%
  filter(year >= 2000) %>% 
  summarise(meteor_count = n())
```

Find the number of meteorites in each year, for every year since 2000.

This approach uses a filter, and uses count to perform the count by year 

```{r}
clean_data %>%
  filter(year >= 2000) %>% 
  count(year)
```

