---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
```


```{r}
books_data <- read_csv("data/books.csv") 
str(books_data)
```


#Investigating the data, exploring the dimensions, missing data and number of distinct values in the dataset 
```{r}
books_data %>% 
summarise(count = is.na(books_data)) 
which(is.na(books_data)) 
n_distinct(books_data)
```


#Dropped the missing values and publisher, isbn and isbn13 
```{r}
clean_books_data <- na.omit(books_data) 
clean_books_data_dropped <- select(clean_books_data, -publisher, -isbn, -isbn13) 

```


#Created a new column that specifies if the number of pages in each book is greater than 1000 or less than 1000 
```{r}
clean_books_data_dropped %>% 
  select(num_pages) %>% 
  mutate(page_number_sum = if_else(num_pages >= 1000, "Greater than or equal to 1000", "Less than 1000")) 
```

#A simple plot of the relationship bewteen book length and book average rating 
#This plot does not really show anything particularly informative, other than the fact the majority of books are between 0 and 1500 pages and most reviews are 3 and above 
```{r}
plot(clean_books_data_dropped$num_pages, clean_books_data_dropped$average_rating) 
```

```{r}
cor(clean_books_data_dropped$num_pages, clean_books_data_dropped$average_rating)
```

#A simple correlation test between number of pages and average rating showed very minimal, if any, correlation - given 0.2 is considered a weak correlation, and 1.0 is a perfect correlation. 

```{r}
library(Hmisc)
```

#Using the Hmisc package to perform pearson and spearman correlation tests 
```{r}
rcorr(clean_books_data_dropped$num_pages, clean_books_data_dropped$average_rating, type=c("pearson"))
```

```{r}
rcorr(clean_books_data_dropped$num_pages, clean_books_data_dropped$average_rating, type=c("spearman"))
```

#How frequently do authors appear in the dataset 
```{r}
clean_books_data_dropped %>% 
  group_by(authors) %>%
  summarise(total_author_appearances = n()) 
```

#Finding the mean average rating for each author and selecting the top 20 average ratings 
```{r}
clean_books_data_dropped %>% 
  group_by(authors) %>% 
  summarise(mean_rating = mean(average_rating)) %>% 
  slice_max(mean_rating, n = 20) 
```
