---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse) 
library(janitor) 
```

```{r}
ames_data <- read_csv("data/ames.csv") %>% 
  clean_names() 
```

Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find? 

The data is right skewed. 

```{r}
lot_area <- ames_data %>%
  summarise(
    mean_lot_area = mean(lot_area), 
) 

lot_area 
```

```{r}
ames_data %>% 
  ggplot(aes(lot_area)) + 
  geom_histogram(bins = 100) 
```

```{r}
library(infer)
```

Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses. 

```{r}
bootstrap_resample_200 <- ames_data %>%
  rep_sample_n(size = 200, replace = TRUE, reps = 5000) %>%
  summarise(
    mean_area = mean(lot_area) 
  ) 

bootstrap_resample_200 
```

```{r}
bootstrap_resample_200 %>%
  ggplot(aes(mean_area)) +
  geom_histogram(col = "white", alpha = 0.7, bins = 100) 
```

Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution 

```{r}
infer_resample <- ames_data %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean") 
```


```{r}
infer_ci_95 <- infer_resample %>%
  get_confidence_interval(level = 0.95, type = "percentile")

infer_ci_95 
```

You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense? 

```{r}
infer_ci_99 <- infer_resample %>%
  get_confidence_interval(level = 0.99, type = "percentile")

infer_ci_99  
```

It is broader. This makes sense because the confidence interval is wider and more of the data falls between these two values and the areas outwith the confidence intervals is smaller. 

Calculate the point estimate of the mean(lot_area) 

```{r}
ames_data %>% 
  summarise(point_est = mean(lot_area) 
) 
```

Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting]. 

I don't think I did this right but the CI and Point Estimate did not change from 200 to 50000 reps for me. 

```{r}
ames_filtered <- ames_data %>% 
  filter(year_built <= 1920)
```

```{r}
bootstrap_resample_date <- ames_filtered %>% 
  specify(response = year_built) %>%
  generate(reps = 50000, type = "bootstrap") %>%
  calculate(stat = "mean") 
```

```{r}
year_ci_95 <- bootstrap_resample_date %>%
  get_confidence_interval(level = 0.95, type = "percentile")

year_ci_95
```

```{r}
point_estimate_50000 <- ames_filtered %>% 
  summarise(point_est = mean(year_built)) 