---
title: "R Notebook"
output: html_notebook
---

---
title: "R Notebook"
output: html_notebook
---

MVP - The Titanic 

You’re going to calculate the conditional probabilities prob( survived ∣ crew ) and prob( survived ∣ passenger ) to settle this dispute. 

```{r}
library(prob)
library(gtools)
library(tidyverse)
```

```{r}
titanic <- read_csv("data/titanic.csv") 
head(titanic) 
```

Recoding the class variable to Passenger and Crew 

```{r}
titanic <- titanic %>% 
  mutate(class = recode(class, "3rd" = "Passenger", 
                                "2nd" = "Passenger", 
                                "1st" = "Passenger", 
                                "engineering crew" = "Crew", 
                                "victualling crew" = "Crew", 
                                "restaurant staff" = "Crew", 
                                "deck crew" = "Crew")) 

```


Calculating the probability of crew that survived 

```{r}
prob_crew_that_survived <- titanic %>%
  filter(class == "Crew", survived == "yes") %>%
  summarise(prob = n() / nrow(titanic)) 

prob_crew_that_survived
```

Calculating the probability of passengers that survived 

```{r}
prob_passengers_that_survived <- titanic %>% 
  filter(class == "Passenger", survived == "yes") %>% 
  summarise(prob = n() / nrow(titanic)) 

prob_passengers_that_survived 
```

Adding a logical column for class. 

```{r}
titanic_mutated <- titanic %>% 
  mutate(is_crew = class == "Crew") 
```

Finding the probability of being a crew member. 

```{r}
prob_crew <- titanic_mutated %>%
  summarise(prob = sum(class == "Crew") / n())
prob_crew 
```

Finding the probability of being a passenger. 

```{r}
prob_passengers <- titanic_mutated %>%
  summarise(prob = sum(class == "Passenger") / n())
prob_passengers
```

By hand the probability of being a crew member and surviving is 0.23707867. So the proportion of crew members that survived was 24%. 

By hand the probability of being a passenger and surviving is 0.37965072. So the probability of passengers that survived was 38%. 

This answers the question and shows passengers were more likely to survive than the crew. 

I could not get this to run in dplyr, I got it to work at one point but then I cleared by global environment and it wouldn't produce the same answer again unfortunately. I've just left my attempts in. 



```{r}
conditional_probability_crew_survivors <- titanic_mutated %>% 
  filter(is_crew == "yes") %>%
  summarise(prob = sum(survived) / n())

conditional_probability_crew_survivors 
```
```{r}
conditional_probability_passenger_survivors <- titanic_mutated %>% 
  filter(survived == "yes") %>%
  summarise(prob = sum(is_crew) / n())

conditional_probability_crew_survivors 
```

```{r}
titanic_mutated <- titanic %>% 
  mutate(is_crew = class == "Crew") %>% 
  mutate(survived_logical = survived == "yes") %>% 
  mutate(is_crew_and_survived = class == "Crew" & survived == "yes") %>% 
  mutate(is_passenger_and_survived = class == "Passenger" & survived == "yes")
```

```{r}
prob_crew_that_survived <- titanic_mutated %>%
  filter(is_crew_and_survived == TRUE) %>% 
  filter(survived == "yes") %>% 
  summarise(prob = sum() / n())

prob_crew_that_survived 
```

```{r}
prob_pasengers_that_survived <- titanic_mutated %>% 
  filter(is_passenger_and_survived == TRUE) %>% 
  summarise(prob = sum(is_crew) / n()) 

prob_pasengers_that_survived 
```

MVP and Extension - Probability problems 

If I roll a six-sided dice once, what is the probability of getting a number less than 5? 

2/3 or 0.6666 

How many outcomes are there in the sample space of an experiment in which we toss three dice? 

```{r}
three_dice <- rolldie(3) 
```

216  

In an experiment where we roll four dice:

how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
what is the probability of this event?
what assumptions do we apply in answering part ii? 

```{r}
four_dice <- rolldie(4) 

total_equals_5_6_7 <- four_dice %>% 
  filter(X1 + X2 + X3 + X4 == 5:7) 
```

9 outcomes. 

```{r}
9 / 1296  
```

The probability of this occuring is 0.006944444. 

The assumption we are making here is that the dice are unbiased. 

Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right? 

```{r}
people <- c("A", "B", "C", "D", "E") 

sitting_chairs <- permutations(n = 5, r = 5, v = people, repeats.allowed = FALSE)
nrow(sitting_chairs) 
```

The probability is 0.008333 

```{r}
six_dice <- rolldie(6) 