---
title: "R Notebook"
output: html_notebook
---

* You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings. 

* We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers. 

* Perform k-means clustering and chose a value of k. 

* Visualise the clustering for your chosen value of k. 

* Do you think the clustering seems a good fit for this data? 

* Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the 'Segmentation & clustering intro' lesson). 

```{r}
library(tidyverse) 
library(broom) 

shopping <- read_csv("mall_customers.csv") %>% 
  janitor::clean_names() %>% 
  select(-customer_id) %>% 
  mutate(gender = recode(gender, "Male" = 0, "Female" = 1)) 

glimpse(shopping) 
```

# Exploring the data 

It appears that those earning under 50k appear to fall in a wide range on the 
spending score. Those earning around 45k to around 60k tend to fall around the 
30 to 60 range. Those earning over about 70k appear to spend a varied amount 
similar to those earning under 50k. Gender does not seem to be a big factor in 
this dataset. 

```{r}
shopping %>% 
  ggplot(aes(annual_income_k, spending_score_1_100, colour = gender)) + 
  geom_point()  

shopping %>% 
  ggplot(aes(age, spending_score_1_100)) + 
  geom_col()  

shopping %>% 
  group_by(gender) %>% 
  summarise(mean_spending = mean(spending_score_1_100)) %>%
  ggplot(aes(gender, mean_spending, fill = gender)) + 
  geom_col() 
```

# Preparing data for clustering and dropping age and gender as these will not be beneficial to the aim of the K-means clustering. 

Scaling the data - gender has been turned into a binary since the k means 
clustering method will not produce good results with categoricals. 

```{r}
summary(shopping) 

shopping_scaled <- shopping %>% 
  select(-c(age, gender)) %>% 
  mutate_all(scale) %>% 

summary(shopping_scaled) 
```

# Performing K-means clustering on the data  

```{r}
shopping_clustered <- kmeans(shopping_scaled, centers = 5, nstart = 25)
shopping_clustered 
```

```{r}
tidy(shopping_clustered, 
     col.names = colnames(shopping_scaled)) 

glance(shopping_clustered) 

augment(shopping_clustered, shopping) 
```

# Determining the K value 

The K value will be 5. 

```{r}
library(factoextra) 

#Unsure what the augment argument is meant to be, it is not accepting a variable name. 

k_clusters <- tibble(k = 1:5) %>%
  mutate(
    kclust = map(k, ~ kmeans(shopping_scaled, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, shopping_scaled)
  ) 

clusterings <- k_clusters %>%
  unnest(glanced)

clusterings 

#Silhouette method 

 silhoutte <- fviz_nbclust(shopping_scaled, kmeans, method = "silhouette", nstart = 25) 

#Elbow Method 

fviz_nbclust(shopping_scaled, kmeans, method = "wss", nstart = 25) 
```

# Visualising clustering 

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k <= 5) %>% 
 ggplot(aes(x = annual_income_k, y = spending_score_1_100)) + 
  geom_point(aes(color = .cluster)) + 
  facet_wrap(~ k) 

clusterings %>% 
  unnest(augmented) %>% 
  filter(k <= 5) %>% 
  group_by(.cluster) %>% 
  summarise(mean(spending_score_1_100), mean(annual_income_k))   
```

The clustering has given a clear distinction between low earners who have a low spending score, low earners with a high income score, those who are in the middle region of income and sit around 50 on the spending score, high earners with a low spending score and high earnings who are spending a lot. I would say this is a pretty accurate way to depict this data given the conclusions drawn earlier are pretty similar to the clustering findings. 